Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
Yay fixed methodology formatting.

%%% I actually think it flows better without having a subsection here..

%\subsection{Question Format} 
%
%\subsubsection{Comprehension Questions} 
%Talk about format here. 
%
%\subsubsection{Wearables Scenarios} 
%Talk about format here. 
%
%\subsubsection{Smartphone Scenarios} 
%Talk about format here. 
%
%\subsubsection{Risk and Benefit Assessment} 
%Talk about format here.

\subsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants.

\subsection{Wearables Scenarios}
%okay, this section is kind of confusing, I must admit..

@@

\subsection{Smartphone Scenarios}
Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone. Unlike the wearables scenario questions, these questions only ask about various situations which may occur using a smartphone, without a <data> or <recipient>. These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et. al's mobile user study \cite{Felt} for eliciting varying reactions from users.

@@

\subsection{Risk and Benefit Assessment}

@@

\subsection{Additional Questions}
The exit portion of the survey consisted of demographics questions to better understand the answers. We included standard demographics questions such as age, gender, and education, but also asked participants if they owned a wearable device to survey the population's exposure to these devices. We also prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences. We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}.

@@

\section{Results}
%confusing runthrough of the results.. is this too packed? 
%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.  Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public. Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat. When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.

>>>>

\subsection{Question Format} 
We talk about the format and justification of the questions from our survey below.

\subsubsection{Comprehension Questions}
Because we were asking questions about a fictitious device, participants were presented with two comprehension questions before the start of the wearable device scenarios questions. These questions served to ensure that participants would be informed of the device which we were going to be referring to, but also served as a filter for people who were inattentive or chose not to answer questions correctly. Filtering incomplete and incorrect responses to either of these comprehension questions filtered out 16\% (n = 366) of our participants.

\subsubsection{Wearables Scenarios}
%okay, this section is kind of confusing, I must admit..

@@

\subsubsection{Smartphone Scenarios}
Following the wearables scenario questions were 2 randomly selected questions from a set of 5 questions on various scenarios which can occur when using a smartphone. Unlike the wearables scenario questions, these questions only ask about various situations which may occur using a smartphone, without a <data> or <recipient>. These five scenarios, ranging from the most upsetting scenario to the least upsetting scenario, were purposefully selected from Felt et. al's mobile user study \cite{Felt} for eliciting varying reactions from users.

@@

\subsubsection{Risk and Benefit Assessment}

@@

\subsubsection{Additional Questions}
The exit portion of the survey consisted of demographics questions to better understand the answers. We included standard demographics questions such as age, gender, and education, but also asked participants if they owned a wearable device to survey the population's exposure to these devices. We also prompted them with an open-ended question on what would be the most likely risks associated with wearable devices, and finished with questions from a privacy index to gauge their privacy preferences. We used the Internet Users' Information Privacy Concerns (IUIPC) index \cite{malhotra2004internet}.

@@

\section{Results}
%%%confusing runthrough of the results.. is this too packed. I wrote a roadmap paragraph instead based on this, which is below. Much better.

%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.  Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public. Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat. When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.
